%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Graduate Student Researcher} % Job title
    {University of California, Davis} % Organization
    {Davis, CA, USA} % Location
    {Aug. 2018 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Investigate the kinetic alterations of myeloid cells in rhesus macaques aging model}
        \item {Determine the effect of aging on the functions of neutrophils and macrophages}
        \item {Investigate the effect of aging on phenotypes and functions of neutrophils and accumulation of PMN-MDSCs}
      \end{cvitems}
    }
%---------------------------------------------------------

  \cventry
    {Dissertation Project} % Job title
    {Tulane National Primate Research Center} % Organization
    {New Orleans, LA, USA} % Location
    {Aug. 2014 - Jul. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Investigated the kinetics of myeloid cells in rhesus macaques during homeostasis}
        \item {Determined the effect of aging on neutrophil kinetics and clearance}
        \item {Determined the effect of aging on phenotypes and functions of neutrophils and accumulation of PMN-MDSCs}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Research Assistant Intern} % Job title
    {China Novartis Institutes for BioMedical Research, Novartis} % Organization
    {Shanghai, China} % Location
    {Jun. 2013 - Sep. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Conducted targeted molecular epidemiology Research on Nasopharyngeal Carcinoma(NPC)}
        \item {Conducted target DNA sequence enrichment experiment(using RainDance RDT1000)}
        \item {Established quality control system for the extracted RNA integrity (using Agilent 2100 RIN score)}
        \item {Established Cell lines from primary cancer tissue using ROCK inhibitors and feeder cells (Georgetown Method).}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Undergraduate Research Project} % Job title
    {Huazhong University of Science and Technology } % Organization
    {Wuhan, China} % Location
    {Jun. 2016 - Dec. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Conducted data analysis and visualization for genome-scale data from The Cancer Genome Atlas (TCGA).}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}